Enter our title here

### 2017-08-14 manuscript.tex
added some how-to

The goal for any introductory statistics course is to help students develope the ability to think statistically 
\citep{AmericanStatisticalAssociation2016}. 
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and simulation.

Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} provide extensive statistical capabilites 
(free of charge) and are commonly used in statistics courses \citep{Chance2007}. R allows students to explore real-world data 
sets which can not only enhance their understanding of concepts, but can also spark an interest in the domain of statistics 
\citep{Wang2017}.

@@

TryR (Code School 2014) is a web-based programs and do not have this reproducible capability. Since public content authoring is not available, educators are limited on what they can teach their students. The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is 
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

DataCamp is also a web application that offers exhisting interactive R programing courses but unlike TryR, educators can 
create their own courses that coincide with the material.

@@

>>>>

The goal for any introductory statistics course is to help students develope the ability to think statistically 
\citep{AmericanStatisticalAssociation2016}. 
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and simulation. Although numerous statistical technologies exist, \textit{R} and \textit{R Studio} 
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R 
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

@@

TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring is not available, educators are limited on what they can teach their students. The R console can be intimidating to introductory statistics students so an advantage of web-based teaching tools is 
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with 
software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

DataCamp is also a web application that offers interactive R programing courses but unlike TryR, educators can 
create their own courses that coincide with the lessons or assign a pre-existing DataCamp course. The DataCamp website offers 
free community courses as well as more specialized classes that you need to purchase. ... (i'll come back to this)

@@

\section{How to Use DataCamp}
Pre-existing courses:
DataCamp has a range of available free community courses that educators can utilize for supplimental R practice.

Creating a DataCamp Course:
To create a course on DataCamp you will first need to create a DataCamp account by visiting website\www.datacamp.com/teach and
have a GitHub account. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are 
make through DataCamp will update the GitHub repository and visa versa. The GitHub repository will contain three files: 
README.md, course.yml, and chapter1.Rmd.
Readme.md contains helpful information of how to get started, citing resourses to learn more about the process. 
course.yml is a file that contains general information about the course you're creating: title, university, description, 
difficulty level, ect.  
chapter1.Rmd is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them chapter1.Rmd, chapter2.Rmd, chapter3.Rmd
ect.

DataCamp courses can contain 3 different types of exercises: Normal, Multiple choice, and video.
